The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-09-29 paper/paper.tex
fix typos

We add noise to the truth values in the extra-galactic catalogues to simulate real observations.
In each case we simulate first year Rubin observations
using the DESC {\sc TXPipe} framework\footnote{\url{https://github.com/LSSTDESC/TXPipe}}.
This follows the methodology of \citet{ivezic_jones_lupton}
and assuming the numerical values for telescope and sky properties therein:
for each galaxy it generates a poisson sample of the number of photons per band based on
its true magnitude, the sky brightness, and instrumental characteristics.
No noise is added to the redshifts of the galaxy; we defer discussion of photometric
redshift uncertainty to future work.

@@

The JAX library provides automatic differentiation of the calculation of the $C_\ell$ values, and so avoids the painful numerical sensitivity which usually affects Fisher matrix calculations. We verified this by comparing the code code to tuned finite difference estimates on CCL spectrum calculations.

>>>>

We add noise to the truth values in the extra-galactic catalogues to simulate real observations.
In each case we simulate first year Rubin observations
using the DESC {\sc TXPipe} framework\footnote{\url{https://github.com/LSSTDESC/TXPipe}}.
This follows the methodology of \citet{ivezic_jones_lupton}
and assuming the numerical values for telescope and sky properties therein:
for each galaxy it generates a Poisson sample of the number of photons per band based on
its true magnitude, the sky brightness, and instrumental characteristics.
No noise is added to the redshifts of the galaxy; we defer discussion of photometric
redshift uncertainty to future work.

@@

The JAX library provides automatic differentiation of the calculation of the $C_\ell$ values, and so avoids the painful numerical sensitivity which usually affects Fisher matrix calculations. We verified this by comparing the code to tuned finite difference estimates on CCL spectrum calculations.
